Re-finding to support a Deep Web Question Answering System

### 2010-03-04 paper/semsearch10/content/qrr.tex
Fixing description of qrr

\section{Query Resolution Recorder (QRR)}
\label{sec:qrr}
% Chris
Answering a question using the deep web requires one to navigate
through a sequence of one or more web pages and links.  Many of the
accesses involve clicks through web forms to resulting pages.  We have
developed a model that represents the various actions a user may carry
out during this process.

During the answer retrieval process, a user discovers an element of
the query's result on a web page.  Next, she highlights that element,
typically a text string.  This highlight allows the QRR to record the
source of the query's answer.  The QRR stores all information from the
user query in our data store.  When the user submits a web form she
may associate each of the form's inputs with one of our stored context
classes.

The discovery process can be broken down into three cases:
\begin{enumerate}
\item The user typed in a URL and highlighted part of or all the
  answer.
\item The user typed in a URL, clicked a link, and found part or all
  of the answer.
\item The user typed in a URL, filled out a form, and found part or
  all of the answer on a subsequent page.
\end{enumerate}

Any discovery process consists of a sequence of these transactions.
Additionally, data collected for inputs and outputs may be found
during any stage of the complete discovery process.  An output
collected during one stage of an extraction may be the input to a
subsequent stage in the extraction.  The QRR builds the completed user
collection process into a QRM.  The following is a mathematical
formulation of information collected for user web interactions.

>>>>

\section{Query Resolution Recorder (QRR)}
\label{sec:qrr}
% Chris
Answering a question using the deep web requires one to navigate
through a sequence of one or more web pages. Many of the accesses involve clicks through web forms or links to resulting pages.  We have developed a model that represents the various actions a user may carry out during this process.

Web interactions can be broken down into three types:
\begin{enumerate}
\item The user highlights text that is needed in the query or forms part of the answer.
\item The user clicks a link.
\item The user fills in and submits a web form. 
\end{enumerate}

When a user submits a web form they are prompted for the classes of each of the form inputs. Here, class refers to categorization of data, e.g. name, date, etc. These classes allow the QRR to map the user's input SSQ tokens (which are also categorized) to their usage in a given form. For a clicked link, the QRR simply records the target url and nothing more. Finally, during the answer retrieval process when a user discovers all or part of the desired information on a web page, she highlights the text in question. This highlight allows the QRR to record the source of the query's answer. All information gathered during the recording process is saved in our data store.

Any query answering process consists of a sequence of these transactions.
Additionally, data collected for inputs and outputs may be found
during any stage of the complete query process.  An output
collected during one stage of an extraction may be the input to a
subsequent stage in the extraction. The QRR builds the completed user
collection process into a Query Resolution Method (QRM).  The following is a mathematical formulation of information collected for user web interactions.
